### 2023-02-02 manuscript.tex
Move FDO spec list to end [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/b789df55763555b00f2320b2c7f1ecd7412e3bc8.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/b789df55763555b00f2320b2c7f1ecd7412e3bc8/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4075295111

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/a122b2bad38efe2c132d867ed52b0f97f1ddabca/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/a122b2bad38efe2c132d867ed52b0f97f1ddabca}{stain/2022-fdo-paper@a122b2b}
on February 2, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/b789df55763555b00f2320b2c7f1ecd7412e3bc8/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/b789df55763555b00f2320b2c7f1ecd7412e3bc8}{stain/2022-fdo-paper@b789df5}
on February 2, 2023.
